Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-25 doc/main_jfm.tex
finished up section 2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of particles suspended in a
two-dimensional unbounded domain $\Omega$. The boundary of each particle
is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2
\cup \cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward
normal. Assuming the inertial terms are negligible, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor).
The process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts. The first part comes
from the hydrophobic attraction potential (HAP). This potential was
introduced in~\cite{Fu20} and models hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
\label{eq:SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$, respectively $1$, representing
hydrophilic, respectively hydrophobic, portions of the surface.  We assume that the $f_i$ and $\Gamma_i$ are
smooth.  The parameter $\rho$ is the
decay length of attraction. The forces and torques for this attraction
are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of Janus particles suspended
in a two-dimensional unbounded domain $\Omega$. The boundary of each
particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup
\Gamma_2 \cup \cdots \cup \Gamma_{N_b}$. Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is the constant viscosity, $p$ is the
pressure, and $\uu_\infty$ is the background flow. Since each particle
$\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu_i$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts. The first part comes
from the hydrophobic attraction potential (HAP). This potential was
introduced in~\cite{Fu20} and models hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b \\
\label{eq:SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$, respectively $1$, representing
hydrophilic, respectively hydrophobic, portions of the surface.  We assume that the $f_i$ and $\Gamma_i$ are
smooth.  The parameter $\rho$ is the
decay length of attraction. The forces and torques for this attraction
are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is the
interfacial tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.
